---
title: "Untitled"
description: |
  A new article created using the Distill format.
author:
  - name: Nora Jones 
    url: https://example.com/norajones
    affiliation: Spacely Sprockets
    affiliation_url: https://example.com/spacelysprokets
date: "`r Sys.Date()`"
bibliography: reference.bib
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Reference

In this example, I have two references: @tourr and @dplyr and I'm wondering if the bibliography processor in distill could standardise the author names to be *surname + given name initial* (i.e. the second one to also show "Wickham, H." rather than "Wickham, Hadley", both inline and at the end). 

I understand this could be done by manually edit the .bib file or add a .csl file, but it would be nice that distill can pick it up by default.

# Spacing between dot points

Also I'm wondering if by default the line spacing between dot points could be smaller by default: 

  - bla bla bla
  - bla bla bla
  
# Possibility for smaller than full text width figure layout

I have notice that there are a few possibilities for wider than full text width layout for figures and am just wondering if there's any option for smaller than full text width. This could be useful if the plot (i.e. the one below) is too large in an article when displayed with the full text width.

```{r}
library(palmerpenguins)
library(magrittr)
library(ggiraph)
library(ggplot2)

out <- penguins %>% 
  ggplot() + 
  geom_point_interactive(
    aes(x = bill_length_mm, y = bill_depth_mm, tooltip = species))

girafe(ggobj = out)
```

